### 2015-12-17 Writeup/submission_v01.tex
added media folder

\documentclass{article} % For LaTeX2e
\usepackage{nips15submit_e,times}
\usepackage{hyperref}
\usepackage{url}
%\documentstyle[nips14submit_09,times,art10]{article} % For LaTeX 2.09

\title{Formatting Instructions for NIPS 2015}

\author{
Alex Brinkman\thanks{ Use footnote for providing further information
about author (webpage, alternative address)---\emph{not} for acknowledging
funding agencies.} \\
Robotics Institute\\
Carnegie Mellon University\\
Pittsburgh, PA 15213 \\
\texttt{abrinkma@andrew.cmu.edu} \\
\And
Coauthor \\
Affiliation \\
Address \\
\texttt{email} \\
\AND
Coauthor \\
Affiliation \\
Address \\
\texttt{email} \\
\And
Coauthor \\
Affiliation \\
Address \\
\texttt{email} \\
\And
Coauthor \\
Affiliation \\
Address \\
\texttt{email} \\
(if needed)\\
}

% The \author macro works with any number of authors. There are two commands
% used to separate the names and addresses of multiple authors: \And and \AND.
%
% Using \And between authors leaves it to \LaTeX{} to determine where to break
% the lines. Using \AND forces a linebreak at that point. So, if \LaTeX{}
% puts 3 of 4 authors names on the first line, and the last on the second
% line, try using \AND instead of \And before the third author name.

\newcommand{\fix}{\marginpar{FIX}}
\newcommand{\new}{\marginpar{NEW}}

%\nipsfinalcopy % Uncomment for camera-ready version

\begin{document}

\maketitle

\begin{abstract}
The abstract paragraph should be indented 1/2~inch (3~picas) on both left and
right-hand margins. Use 10~point type, with a vertical spacing of 11~points.
The word \textbf{Abstract} must be centered, bold, and in point size 12. Two
line spaces precede the abstract. The abstract must be limited to one
paragraph.
\end{abstract}

\section{Submission of papers to NIPS 2015}

NIPS requires electronic submissions.  The electronic submission site is  
\begin{center}
   \url{http://papers.nips.cc}
\end{center}

Please read carefully the
instructions below, and follow them faithfully.
\subsection{Style}

Papers to be submitted to NIPS 2015 must be prepared according to the
instructions presented here. Papers may be only up to eight pages long,
including figures. Since 2009 an additional ninth page \textit{containing only
cited references} is allowed. Papers that exceed nine pages will not be
reviewed, or in any other way considered for presentation at the conference.
%This is a strict upper bound.

Please note that this year we have introduced automatic line number generation
into the style file (for \LaTeXe and Word versions). This is to help reviewers
refer to specific lines of the paper when they make their comments. Please do
NOT refer to these line numbers in your paper as they will be removed from the
style file for the final version of accepted papers.

The margins in 2015 are the same as since 2007, which allow for $\approx 15\%$
more words in the paper compared to earlier years. We are also again using 
double-blind reviewing. Both of these require the use of new style files.

Authors are required to use the NIPS \LaTeX{} style files obtainable at the
NIPS website as indicated below. Please make sure you use the current files and
not previous versions. Tweaking the style files may be grounds for rejection.

%% \subsection{Double-blind reviewing}

%% This year we are doing double-blind reviewing: the reviewers will not know 
%% who the authors of the paper are. For submission, the NIPS style file will 
%% automatically anonymize the author list at the beginning of the paper.

%% Please write your paper in such a way to preserve anonymity. Refer to
%% previous work by the author(s) in the third person, rather than first
%% person. Do not provide Web links to supporting material at an identifiable
%% web site.

%%\subsection{Electronic submission}
%%
%% \textbf{THE SUBMISSION DEADLINE IS June 5, 2015. SUBMISSIONS MUST BE LOGGED BY
%% 23:00, June 5, 2015, UNIVERSAL TIME}

%% You must enter your submission in the electronic submission form available at
%% the NIPS website listed above. You will be asked to enter paper title, name of
%% all authors, keyword(s), and data about the contact
%% author (name, full address, telephone, fax, and email). You will need to
%% upload an electronic (postscript or pdf) version of your paper.

%% You can upload more than one version of your paper, until the
%% submission deadline. We strongly recommended uploading your paper in
%% advance of the deadline, so you can avoid last-minute server congestion.
%%
%% Note that your submission is only valid if you get an e-mail
%% confirmation from the server. If you do not get such an e-mail, please
%% try uploading again.

\subsection{Retrieval of style files}

The style files for NIPS and other conference information are available on the World Wide Web at
\begin{center}
   \url{http://www.nips.cc/}
\end{center}
The file \verb+nips2015.pdf+ contains these 
instructions and illustrates the
various formatting requirements your NIPS paper must satisfy. \LaTeX{}
users can choose between two style files:
\verb+nips15submit_09.sty+ (to be used with \LaTeX{} version 2.09) and
\verb+nips15submit_e.sty+ (to be used with \LaTeX{}2e). The file
\verb+nips2015.tex+ may be used as a ``shell'' for writing your paper. All you
have to do is replace the author, title, abstract, and text of the paper with
your own. The file
\verb+nips2015.rtf+ is provided as a shell for MS Word users.

The formatting instructions contained in these style files are summarized in
sections \ref{gen_inst}, \ref{headings}, and \ref{others} below.

%% \subsection{Keywords for paper submission}
%% Your NIPS paper can be submitted with any of the following keywords (more than one keyword is possible for each paper):

%% \begin{verbatim}
%% Bioinformatics
%% Biological Vision
%% Brain Imaging and Brain Computer Interfacing
%% Clustering
%% Cognitive Science
%% Control and Reinforcement Learning
%% Dimensionality Reduction and Manifolds
%% Feature Selection
%% Gaussian Processes
%% Graphical Models
%% Hardware Technologies
%% Kernels
%% Learning Theory
%% Machine Vision
%% Margins and Boosting
%% Neural Networks
%% Neuroscience
%% Other Algorithms and Architectures
%% Other Applications
%% Semi-supervised Learning
%% Speech and Signal Processing
%% Text and Language Applications

%% \end{verbatim}

\section{General formatting instructions}
\label{gen_inst}

The text must be confined within a rectangle 5.5~inches (33~picas) wide and
9~inches (54~picas) long. The left margin is 1.5~inch (9~picas).
Use 10~point type with a vertical spacing of 11~points. Times New Roman is the
preferred typeface throughout. Paragraphs are separated by 1/2~line space,
with no indentation.

Paper title is 17~point, initial caps/lower case, bold, centered between
2~horizontal rules. Top rule is 4~points thick and bottom rule is 1~point
thick. Allow 1/4~inch space above and below title to rules. All pages should
start at 1~inch (6~picas) from the top of the page.

%The version of the paper submitted for review should have ``Anonymous Author(s)'' as the author of the paper.

For the final version, authors' names are
set in boldface, and each name is centered above the corresponding
address. The lead author's name is to be listed first (left-most), and
the co-authors' names (if different address) are set to follow. If
there is only one co-author, list both author and co-author side by side.

Please pay special attention to the instructions in section \ref{others}
regarding figures, tables, acknowledgments, and references.

\section{Headings: first level}
\label{headings}

First level headings are lower case (except for first word and proper nouns),
flush left, bold and in point size 12. One line space before the first level
heading and 1/2~line space after the first level heading.

\subsection{Headings: second level}

Second level headings are lower case (except for first word and proper nouns),
flush left, bold and in point size 10. One line space before the second level
heading and 1/2~line space after the second level heading.

\subsubsection{Headings: third level}

Third level headings are lower case (except for first word and proper nouns),
flush left, bold and in point size 10. One line space before the third level
heading and 1/2~line space after the third level heading.

\section{Citations, figures, tables, references}
\label{others}

These instructions apply to everyone, regardless of the formatter being used.

\subsection{Citations within the text}

Citations within the text should be numbered consecutively. The corresponding
number is to appear enclosed in square brackets, such as [1] or [2]-[5]. The
corresponding references are to be listed in the same order at the end of the
paper, in the \textbf{References} section. (Note: the standard
\textsc{Bib\TeX} style \texttt{unsrt} produces this.) As to the format of the
references themselves, any style is acceptable as long as it is used
consistently.

As submission is double blind, refer to your own published work in the 
third person. That is, use ``In the previous work of Jones et al.\ [4]'',
not ``In our previous work [4]''. If you cite your other papers that
are not widely available (e.g.\ a journal paper under review), use
anonymous author names in the citation, e.g.\ an author of the
form ``A.\ Anonymous''.

\subsection{Footnotes}

Indicate footnotes with a number\footnote{Sample of the first footnote} in the
text. Place the footnotes at the bottom of the page on which they appear.
Precede the footnote with a horizontal rule of 2~inches
(12~picas).\footnote{Sample of the second footnote}

\subsection{Figures}

All artwork must be neat, clean, and legible. Lines should be dark
enough for purposes of reproduction; art work should not be
hand-drawn. The figure number and caption always appear after the
figure. Place one line space before the figure caption, and one line
space after the figure. The figure caption is lower case (except for
first word and proper nouns); figures are numbered consecutively.

Make sure the figure caption does not get separated from the figure.
Leave sufficient space to avoid splitting the figure and figure caption.

You may use color figures. 
However, it is best for the
figure captions and the paper body to make sense if the paper is printed
either in black/white or in color.
\begin{figure}[h]
\begin{center}
%\framebox[4.0in]{$\;$}
\fbox{\rule[-.5cm]{0cm}{4cm} \rule[-.5cm]{4cm}{0cm}}
\end{center}
\caption{Sample figure caption.}
\end{figure}

\subsection{Tables}

All tables must be centered, neat, clean and legible. Do not use hand-drawn
tables. The table number and title always appear before the table. See
Table~\ref{sample-table}.

Place one line space before the table title, one line space after the table
title, and one line space after the table. The table title must be lower case
(except for first word and proper nouns); tables are numbered consecutively.

\begin{table}[t]
\caption{Sample table title}
\label{sample-table}
\begin{center}
\begin{tabular}{ll}
\multicolumn{1}{c}{\bf PART}  &\multicolumn{1}{c}{\bf DESCRIPTION}
\\ \hline \\
Dendrite         &Input terminal \\
Axon             &Output terminal \\
Soma             &Cell body (contains cell nucleus) \\
\end{tabular}
\end{center}
\end{table}

\section{Final instructions}
Do not change any aspects of the formatting parameters in the style files.
In particular, do not modify the width or length of the rectangle the text
should fit into, and do not change font sizes (except perhaps in the
\textbf{References} section; see below). Please note that pages should be
numbered.

\section{Preparing PostScript or PDF files}

Please prepare PostScript or PDF files with paper size ``US Letter'', and
not, for example, ``A4''. The -t
letter option on dvips will produce US Letter files.

Fonts were the main cause of problems in the past years. Your PDF file must
only contain Type 1 or Embedded TrueType fonts. Here are a few instructions
to achieve this.

\begin{itemize}

\item You can check which fonts a PDF files uses.  In Acrobat Reader,
select the menu Files$>$Document Properties$>$Fonts and select Show All Fonts. You can
also use the program \verb+pdffonts+ which comes with \verb+xpdf+ and is
available out-of-the-box on most Linux machines.

\item The IEEE has recommendations for generating PDF files whose fonts
are also acceptable for NIPS. Please see
\url{http://www.emfield.org/icuwb2010/downloads/IEEE-PDF-SpecV32.pdf}

\item LaTeX users:

\begin{itemize}

\item Consider directly generating PDF files using \verb+pdflatex+
(especially if you are a MiKTeX user). 
PDF figures must be substituted for EPS figures, however.

\item Otherwise, please generate your PostScript and PDF files with the following commands:
\begin{verbatim} 
dvips mypaper.dvi -t letter -Ppdf -G0 -o mypaper.ps
ps2pdf mypaper.ps mypaper.pdf
\end{verbatim}

Check that the PDF files only contains Type 1 fonts. 
%For the final version, please send us both the Postscript file and
%the PDF file.

\item xfig "patterned" shapes are implemented with 
bitmap fonts.  Use "solid" shapes instead. 
\item The \verb+\bbold+ package almost always uses bitmap
fonts.  You can try the equivalent AMS Fonts with command
\begin{verbatim}
\usepackage[psamsfonts]{amssymb}
\end{verbatim}
 or use the following workaround for reals, natural and complex: 
\begin{verbatim}
\newcommand{\RR}{I\!\!R} %real numbers
\newcommand{\Nat}{I\!\!N} %natural numbers 
\newcommand{\CC}{I\!\!\!\!C} %complex numbers
\end{verbatim}

\item Sometimes the problematic fonts are used in figures
included in LaTeX files. The ghostscript program \verb+eps2eps+ is the simplest
way to clean such figures. For black and white figures, slightly better
results can be achieved with program \verb+potrace+.
\end{itemize}
\item MSWord and Windows users (via PDF file):
\begin{itemize}
\item Install the Microsoft Save as PDF Office 2007 Add-in from
\url{http://www.microsoft.com/downloads/details.aspx?displaylang=en\&familyid=4d951911-3e7e-4ae6-b059-a2e79ed87041}
\item Select ``Save or Publish to PDF'' from the Office or File menu
\end{itemize}
\item MSWord and Mac OS X users (via PDF file):
\begin{itemize}
\item From the print menu, click the PDF drop-down box, and select ``Save
as PDF...''
\end{itemize}
\item MSWord and Windows users (via PS file):
\begin{itemize}
\item To create a new printer
on your computer, install the AdobePS printer driver and the Adobe Distiller PPD file from
\url{http://www.adobe.com/support/downloads/detail.jsp?ftpID=204} {\it Note:} You must reboot your PC after installing the
AdobePS driver for it to take effect.
\item To produce the ps file, select ``Print'' from the MS app, choose
the installed AdobePS printer, click on ``Properties'', click on ``Advanced.''
\item Set ``TrueType Font'' to be ``Download as Softfont''
\item Open the ``PostScript Options'' folder
\item Select ``PostScript Output Option'' to be ``Optimize for Portability''
\item Select ``TrueType Font Download Option'' to be ``Outline''
\item Select ``Send PostScript Error Handler'' to be ``No''
\item Click ``OK'' three times, print your file.
\item Now, use Adobe Acrobat Distiller or ps2pdf to create a PDF file from
the PS file. In Acrobat, check the option ``Embed all fonts'' if
applicable.
\end{itemize}

\end{itemize}
If your file contains Type 3 fonts or non embedded TrueType fonts, we will
ask you to fix it.

\subsection{Margins in LaTeX}

Most of the margin problems come from figures positioned by hand using
\verb+\special+ or other commands. We suggest using the command
\verb+\includegraphics+
from the graphicx package. Always specify the figure width as a multiple of
the line width as in the example below using .eps graphics
\begin{verbatim}
   \usepackage[dvips]{graphicx} ... 
   \includegraphics[width=0.8\linewidth]{myfile.eps} 
\end{verbatim}
or % Apr 2009 addition
\begin{verbatim}
   \usepackage[pdftex]{graphicx} ... 
   \includegraphics[width=0.8\linewidth]{myfile.pdf} 
\end{verbatim}
for .pdf graphics. 
See section 4.4 in the graphics bundle documentation (\url{http://www.ctan.org/tex-archive/macros/latex/required/graphics/grfguide.ps})

A number of width problems arise when LaTeX cannot properly hyphenate a
line. Please give LaTeX hyphenation hints using the \verb+\-+ command.

\subsubsection*{Acknowledgments}

Use unnumbered third level headings for the acknowledgments. All
acknowledgments go at the end of the paper. Do not include 
acknowledgments in the anonymized submission, only in the 
final paper.

\subsubsection*{References}

References follow the acknowledgments. Use unnumbered third level heading for
the references. Any choice of citation style is acceptable as long as you are
consistent. It is permissible to reduce the font size to `small' (9-point) 
when listing the references. {\bf Remember that this year you can use
a ninth page as long as it contains \emph{only} cited references.}

\small{
[1] Alexander, J.A. \& Mozer, M.C. (1995) Template-based algorithms
for connectionist rule extraction. In G. Tesauro, D. S. Touretzky
and T.K. Leen (eds.), {\it Advances in Neural Information Processing
Systems 7}, pp. 609-616. Cambridge, MA: MIT Press.

[2] Bower, J.M. \& Beeman, D. (1995) {\it The Book of GENESIS: Exploring
Realistic Neural Models with the GEneral NEural SImulation System.}
New York: TELOS/Springer-Verlag.

[3] Hasselmo, M.E., Schnell, E. \& Barkai, E. (1995) Dynamics of learning
and recall at excitatory recurrent synapses and cholinergic modulation
in rat hippocampal region CA3. {\it Journal of Neuroscience}
{\bf 15}(7):5249-5262.
}

\end{document}

### 2015-12-17 src/elasticnet_optimization.py

@@ -1,0 +1,85 @@
+# -*- coding: utf-8 -*-
+
+import numpy as np
+import scipy.io as sio
+import matplotlib.pyplot as plt
+import numpy as np
+import time
+
+from sklearn.cross_validation import KFold
+from sklearn import svm
+from sklearn.feature_selection import SelectKBest
+from sklearn.decomposition import PCA
+from sklearn import cross_validation
+from sklearn.cross_validation import StratifiedKFold
+from sklearn import preprocessing
+from sklearn.feature_selection import SelectKBest
+from sklearn.pipeline import Pipeline, FeatureUnion
+import matplotlib.cm as cm
+#from sklearn.kernel_ridge import KernelRidge
+from sklearn.linear_model import Ridge, MultiTaskElasticNetCV, Lasso, MultiTaskLassoCV
+
+''' Notes
+        
+    Results
+    model.alpha_ = 0.62570190237998946
+    
+    
+    
+end Notes'''
+
+file_loc = '/home/apark/Homework/ML_Project2/data/'
+
+## Import data
+import_test = sio.loadmat(file_loc + 'Test.mat')
+import_train = sio.loadmat(file_loc + 'Train.mat')
+import_providedidx = sio.loadmat(file_loc + 'provideIdx.mat')
+import_missidx = sio.loadmat(file_loc + 'missIdx.mat')
+import_providedata = sio.loadmat(file_loc + 'provideData_1000.mat')
+import_events = sio.loadmat(file_loc + 'events_1000.mat')
+import_test_labels = sio.loadmat(file_loc + 'Ytest.mat')
+
+provideIdx = import_providedidx['provideIdx'] - 1 # since Matlab indexing starts at 1
+provideIdx = provideIdx.ravel()
+missIdx = import_missidx['missIdx'] - 1 # since Matlab indexing starts at 1
+missIdx = missIdx.ravel()
+events = import_events['events']
+X_test_raw_1 = import_test['Xtest']
+X_test_raw = import_providedata['provideData'] # size = (1000, 3172)
+XY_train_raw = import_train['Xtrain']
+X_train_raw_2 = XY_train_raw[:,provideIdx] # size = (500, 3172)
+X_train_raw_1 = X_test_raw_1[:,provideIdx]  
+Y_train_raw_2 = XY_train_raw[:,missIdx] # size = (500, 2731)
+Y_train_raw_1 = X_test_raw_1[:,missIdx]
[…]

### 2015-12-17 Writeup/submission_v01.tex
added part 3 and latex changes

@@
 
-\title{Formatting Instructions for NIPS 2015}
+\title{Machine Learning Project}
 
 \author{
-Alex Brinkman\thanks{ Use footnote for providing further information
-about author (webpage, alternative address)---\emph{not} for acknowledging
-funding agencies.} \\
+Alex Brinkman\\
 Robotics Institute\\
@@
 \And
-Coauthor \\
-Affiliation \\
-Address \\
-\texttt{email} \\
-\AND
-Coauthor \\
-Affiliation \\
-Address \\
-\texttt{email} \\
-\And
-Coauthor \\
-Affiliation \\
-Address \\
-\texttt{email} \\
-\And
-Coauthor \\
-Affiliation \\
-Address \\
-\texttt{email} \\
-(if needed)\\
+Abhishek Bhatia \\
+Robotics Institute \\
+Carnegie Mellon University\\
+Pittsburgh, PA 15213 \\
+\texttt{abhatia1@andrew.cmu.edu} \\
 }
@@
 
-%\nipsfinalcopy % Uncomment for camera-ready version
+\nipsfinalcopy % Uncomment for camera-ready version
 
@@
 \begin{abstract}
-The abstract paragraph should be indented 1/2~inch (3~picas) on both left and
-right-hand margins. Use 10~point type, with a vertical spacing of 11~points.
-The word \textbf{Abstract} must be centered, bold, and in point size 12. Two
-line spaces precede the abstract. The abstract must be limited to one
-paragraph.
+abstract goes here
 \end{abstract}
 
-\section{Submission of papers to NIPS 2015}
+\section{Part 1}
 
-NIPS requires electronic submissions.  The electronic submission site is  
-\begin{center}
-   \url{http://papers.nips.cc}
-\end{center}
-
-Please read carefully the
-instructions below, and follow them faithfully.
+The goal of the project for part 1 is to classify subject behavior baed on raw voxel activation values.
+The final approach developed to achieve this goal includes an SVM classifier, custom feature extraction, and a voting method.
+The resulting accuracy was 60.47\% on the holdout data set
 \subsection{Style}

### 2015-12-17 part3/part3.py

@@ -1,0 +1,95 @@
+# -*- coding: utf-8 -*-
+
+import numpy as np
+import scipy.io as sio
+import matplotlib.pyplot as plt
+import numpy as np
+from sklearn.cross_validation import KFold
+from sklearn import svm
+from sklearn.feature_selection import SelectKBest
+from sklearn.decomposition import PCA
+from sklearn import cross_validation
+from sklearn.cross_validation import StratifiedKFold
+from sklearn import preprocessing
+from sklearn.feature_selection import SelectKBest
+from sklearn.pipeline import Pipeline, FeatureUnion
+import matplotlib.cm as cm
+
+file_loc = '/home/apark/Homework/ML_Project2/data/'
+
+## Import data
+import_test = sio.loadmat(file_loc + 'Test.mat')
+import_train = sio.loadmat(file_loc + 'Train.mat')
+import_providedidx = sio.loadmat(file_loc + 'provideIdx.mat')
+import_missidx = sio.loadmat(file_loc + 'missIdx.mat')
+import_providedata = sio.loadmat(file_loc + 'provideData_1000.mat')
+import_events = sio.loadmat(file_loc + 'events_1000.mat')
+import_test_labels = sio.loadmat(file_loc + 'Ytest.mat')
+
+provideIdx = import_providedidx['provideIdx'] - 1 # since Matlab indexing starts at 1
+provideIdx = provideIdx.ravel()
+missIdx = import_missidx['missIdx'] - 1 # since Matlab indexing starts at 1
+missIdx = missIdx.ravel()
+events = import_events['events']
+X_test_raw_1 = import_test['Xtest']
+X_test_raw = import_providedata['provideData'] # size = (1000, 3172)
+XY_train_raw = import_train['Xtrain']
+X_train_raw_2 = XY_train_raw[:,provideIdx] # size = (500, 3172)
+X_train_raw_1 = X_test_raw_1[:,provideIdx]  
+X_train_raw = np.vstack((X_train_raw_1, X_train_raw_2))
+train_labels = np.vstack((import_test_labels['Ytest'],import_train['Ytrain'])) #labels of the original train data
+
+## Standardization
+scaler = preprocessing.StandardScaler().fit(X_train_raw)
+X_train_scaled = scaler.transform(X_train_raw)
+
+## PCA and Feature Selection
[…]

### 2015-12-17 Writeup/submission_v01.tex
added figues, references, and table to latex doc

@@
 \usepackage{url}
+\usepackage{graphicx}
 %\documentstyle[nips14submit_09,times,art10]{article} % For LaTeX 2.09
@@
 The final approach developed to achieve this goal includes an SVM classifier, custom feature extraction, and a voting method.
-The resulting accuracy was 60.47\% on the holdout data set
-\subsection{Style}
+The resulting accuracy was 60.47\% on the holdout data set.
+\subsection{SVM Classifier}
+Abhishek
+\subsection{Custom Feature Extraction}
 
-Papers to be submitted to NIPS 2015 must be prepared according to the
-instructions presented here. Papers may be only up to eight pages long,
-including figures. Since 2009 an additional ninth page \textit{containing only
-cited references} is allowed. Papers that exceed nine pages will not be
-reviewed, or in any other way considered for presentation at the conference.
-%This is a strict upper bound.
+The custom feature extraction....
 
-Please note that this year we have introduced automatic line number generation
-into the style file (for \LaTeXe and Word versions). This is to help reviewers
-refer to specific lines of the paper when they make their comments. Please do
-NOT refer to these line numbers in your paper as they will be removed from the
-style file for the final version of accepted papers.
-
-The margins in 2015 are the same as since 2007, which allow for $\approx 15\%$
-more words in the paper compared to earlier years. We are also again using 
-double-blind reviewing. Both of these require the use of new style files.
-
-Authors are required to use the NIPS \LaTeX{} style files obtainable at the
-NIPS website as indicated below. Please make sure you use the current files and
-not previous versions. Tweaking the style files may be grounds for rejection.
-
-%% \subsection{Double-blind reviewing}
-
-%% This year we are doing double-blind reviewing: the reviewers will not know 
-%% who the authors of the paper are. For submission, the NIPS style file will 
-%% automatically anonymize the author list at the beginning of the paper.
-
-%% Please write your paper in such a way to preserve anonymity. Refer to
-%% previous work by the author(s) in the third person, rather than first
-%% person. Do not provide Web links to supporting material at an identifiable
-%% web site.
-
-%%\subsection{Electronic submission}
-%%
-%% \textbf{THE SUBMISSION DEADLINE IS June 5, 2015. SUBMISSIONS MUST BE LOGGED BY
-%% 23:00, June 5, 2015, UNIVERSAL TIME}
-
-%% You must enter your submission in the electronic submission form available at
-%% the NIPS website listed above. You will be asked to enter paper title, name of
-%% all authors, keyword(s), and data about the contact
-%% author (name, full address, telephone, fax, and email). You will need to
-%% upload an electronic (postscript or pdf) version of your paper.
-
-%% You can upload more than one version of your paper, until the
-%% submission deadline. We strongly recommended uploading your paper in
-%% advance of the deadline, so you can avoid last-minute server congestion.
-%%
-%% Note that your submission is only valid if you get an e-mail
-%% confirmation from the server. If you do not get such an e-mail, please
-%% try uploading again.
-
-\subsection{Retrieval of style files}
-
-The style files for NIPS and other conference information are available on the World Wide Web at
-\begin{center}
-   \url{http://www.nips.cc/}
-\end{center}
-The file \verb+nips2015.pdf+ contains these 
-instructions and illustrates the
-various formatting requirements your NIPS paper must satisfy. \LaTeX{}
-users can choose between two style files:
-\verb+nips15submit_09.sty+ (to be used with \LaTeX{} version 2.09) and
-\verb+nips15submit_e.sty+ (to be used with \LaTeX{}2e). The file
-\verb+nips2015.tex+ may be used as a ``shell'' for writing your paper. All you
-have to do is replace the author, title, abstract, and text of the paper with
-your own. The file
-\verb+nips2015.rtf+ is provided as a shell for MS Word users.
-
-The formatting instructions contained in these style files are summarized in
-sections \ref{gen_inst}, \ref{headings}, and \ref{others} below.
-
-%% \subsection{Keywords for paper submission}
-%% Your NIPS paper can be submitted with any of the following keywords (more than one keyword is possible for each paper):
-
-%% \begin{verbatim}
-%% Bioinformatics
-%% Biological Vision
-%% Brain Imaging and Brain Computer Interfacing
-%% Clustering
-%% Cognitive Science
-%% Control and Reinforcement Learning
-%% Dimensionality Reduction and Manifolds
-%% Feature Selection
-%% Gaussian Processes
-%% Graphical Models
-%% Hardware Technologies
-%% Kernels
-%% Learning Theory
-%% Machine Vision
-%% Margins and Boosting
-%% Neural Networks
-%% Neuroscience
-%% Other Algorithms and Architectures
-%% Other Applications
-%% Semi-supervised Learning
-%% Speech and Signal Processing
-%% Text and Language Applications
-
-%% \end{verbatim}
-
-\section{General formatting instructions}
-\label{gen_inst}
-
-The text must be confined within a rectangle 5.5~inches (33~picas) wide and
-9~inches (54~picas) long. The left margin is 1.5~inch (9~picas).
-Use 10~point type with a vertical spacing of 11~points. Times New Roman is the
-preferred typeface throughout. Paragraphs are separated by 1/2~line space,
-with no indentation.
-
-Paper title is 17~point, initial caps/lower case, bold, centered between
-2~horizontal rules. Top rule is 4~points thick and bottom rule is 1~point
-thick. Allow 1/4~inch space above and below title to rules. All pages should
-start at 1~inch (6~picas) from the top of the page.
-
-%The version of the paper submitted for review should have ``Anonymous Author(s)'' as the author of the paper.
-
-For the final version, authors' names are
-set in boldface, and each name is centered above the corresponding
-address. The lead author's name is to be listed first (left-most), and
-the co-authors' names (if different address) are set to follow. If
-there is only one co-author, list both author and co-author side by side.
-
-Please pay special attention to the instructions in section \ref{others}
-regarding figures, tables, acknowledgments, and references.
-
-\section{Headings: first level}
-\label{headings}
-
-First level headings are lower case (except for first word and proper nouns),
-flush left, bold and in point size 12. One line space before the first level
-heading and 1/2~line space after the first level heading.
-
-\subsection{Headings: second level}
-
-Second level headings are lower case (except for first word and proper nouns),
-flush left, bold and in point size 10. One line space before the second level
-heading and 1/2~line space after the second level heading.
-
-\subsubsection{Headings: third level}
-
-Third level headings are lower case (except for first word and proper nouns),
-flush left, bold and in point size 10. One line space before the third level
-heading and 1/2~line space after the third level heading.
-
-\section{Citations, figures, tables, references}
-\label{others}
-
-These instructions apply to everyone, regardless of the formatter being used.
-
-\subsection{Citations within the text}
-
-Citations within the text should be numbered consecutively. The corresponding
-number is to appear enclosed in square brackets, such as [1] or [2]-[5]. The
-corresponding references are to be listed in the same order at the end of the
-paper, in the \textbf{References} section. (Note: the standard
-\textsc{Bib\TeX} style \texttt{unsrt} produces this.) As to the format of the
-references themselves, any style is acceptable as long as it is used
-consistently.
-
-As submission is double blind, refer to your own published work in the 
-third person. That is, use ``In the previous work of Jones et al.\ [4]'',
-not ``In our previous work [4]''. If you cite your other papers that
-are not widely available (e.g.\ a journal paper under review), use
-anonymous author names in the citation, e.g.\ an author of the
-form ``A.\ Anonymous''.
-
-\subsection{Footnotes}
-
-Indicate footnotes with a number\footnote{Sample of the first footnote} in the
-text. Place the footnotes at the bottom of the page on which they appear.
-Precede the footnote with a horizontal rule of 2~inches
-(12~picas).\footnote{Sample of the second footnote}
-
-\subsection{Figures}
-
-All artwork must be neat, clean, and legible. Lines should be dark
-enough for purposes of reproduction; art work should not be
-hand-drawn. The figure number and caption always appear after the
-figure. Place one line space before the figure caption, and one line
-space after the figure. The figure caption is lower case (except for
-first word and proper nouns); figures are numbered consecutively.
-
-Make sure the figure caption does not get separated from the figure.
-Leave sufficient space to avoid splitting the figure and figure caption.
-
-You may use color figures. 
-However, it is best for the
-figure captions and the paper body to make sense if the paper is printed
-either in black/white or in color.
 \begin{figure}[h]
@@
 %\framebox[4.0in]{$\;$}
-\fbox{\rule[-.5cm]{0cm}{4cm} \rule[-.5cm]{4cm}{0cm}}
+\includegraphics[scale=.5]{media/cross_validation_figure_2.png}
 \end{center}
@@
 \end{figure}
-
-\subsection{Tables}
-
-All tables must be centered, neat, clean and legible. Do not use hand-drawn
-tables. The table number and title always appear before the table. See
-Table~\ref{sample-table}.
-
-Place one line space before the table title, one line space after the table
-title, and one line space after the table. The table title must be lower case
-(except for first word and proper nouns); tables are numbered consecutively.
 
@@
 \begin{tabular}{ll}
-\multicolumn{1}{c}{\bf PART}  &\multicolumn{1}{c}{\bf DESCRIPTION}
+\multicolumn{1}{c}{\bf HEADING C1}  &\multicolumn{1}{c}{\bf HEADING C2}
 \\ \hline \\
-Dendrite         &Input terminal \\
-Axon             &Output terminal \\
-Soma             &Cell body (contains cell nucleus) \\
+r1c1   &r1c2       \\
+r2c1   &r2c2 \\
+etc		&etc\\
 \end{tabular}
@@
 
-\section{Final instructions}
-Do not change any aspects of the formatting parameters in the style files.
-In particular, do not modify the width or length of the rectangle the text
-should fit into, and do not change font sizes (except perhaps in the
-\textbf{References} section; see below). Please note that pages should be
-numbered.
+\subsection{Voting Method}
 
-\section{Preparing PostScript or PDF files}
+\section{Part 2}
+\subsection{Ridge and Lasso Classifiers}
+\subsection{MultiTaskLasso Cross Validation}
+\subsection{Euclidean Clustering}
 
-Please prepare PostScript or PDF files with paper size ``US Letter'', and
-not, for example, ``A4''. The -t
-letter option on dvips will produce US Letter files.
+\section{Part 3}
 
-Fonts were the main cause of problems in the past years. Your PDF file must
-only contain Type 1 or Embedded TrueType fonts. Here are a few instructions
-to achieve this.
+\subsection{Hypothesis}
 
-\begin{itemize}
+\subsection{Experiment}
 
-\item You can check which fonts a PDF files uses.  In Acrobat Reader,
-select the menu Files$>$Document Properties$>$Fonts and select Show All Fonts. You can
-also use the program \verb+pdffonts+ which comes with \verb+xpdf+ and is
-available out-of-the-box on most Linux machines.
-
-\item The IEEE has recommendations for generating PDF files whose fonts
-are also acceptable for NIPS. Please see
-\url{http://www.emfield.org/icuwb2010/downloads/IEEE-PDF-SpecV32.pdf}
-
-\item LaTeX users:
-
-\begin{itemize}
-
-\item Consider directly generating PDF files using \verb+pdflatex+
-(especially if you are a MiKTeX user). 
-PDF figures must be substituted for EPS figures, however.
-
-\item Otherwise, please generate your PostScript and PDF files with the following commands:
-\begin{verbatim} 
-dvips mypaper.dvi -t letter -Ppdf -G0 -o mypaper.ps
-ps2pdf mypaper.ps mypaper.pdf
-\end{verbatim}
-
-Check that the PDF files only contains Type 1 fonts. 
-%For the final version, please send us both the Postscript file and
-%the PDF file.
-
-\item xfig "patterned" shapes are implemented with 
-bitmap fonts.  Use "solid" shapes instead. 
-\item The \verb+\bbold+ package almost always uses bitmap
-fonts.  You can try the equivalent AMS Fonts with command
-\begin{verbatim}
-\usepackage[psamsfonts]{amssymb}
-\end{verbatim}
- or use the following workaround for reals, natural and complex: 
-\begin{verbatim}
-\newcommand{\RR}{I\!\!R} %real numbers
-\newcommand{\Nat}{I\!\!N} %natural numbers 
-\newcommand{\CC}{I\!\!\!\!C} %complex numbers
-\end{verbatim}
-
-\item Sometimes the problematic fonts are used in figures
-included in LaTeX files. The ghostscript program \verb+eps2eps+ is the simplest
-way to clean such figures. For black and white figures, slightly better
-results can be achieved with program \verb+potrace+.
-\end{itemize}
-\item MSWord and Windows users (via PDF file):
-\begin{itemize}
-\item Install the Microsoft Save as PDF Office 2007 Add-in from
-\url{http://www.microsoft.com/downloads/details.aspx?displaylang=en\&familyid=4d951911-3e7e-4ae6-b059-a2e79ed87041}
-\item Select ``Save or Publish to PDF'' from the Office or File menu
-\end{itemize}
-\item MSWord and Mac OS X users (via PDF file):
-\begin{itemize}
-\item From the print menu, click the PDF drop-down box, and select ``Save
-as PDF...''
-\end{itemize}
-\item MSWord and Windows users (via PS file):
-\begin{itemize}
-\item To create a new printer
-on your computer, install the AdobePS printer driver and the Adobe Distiller PPD file from
-\url{http://www.adobe.com/support/downloads/detail.jsp?ftpID=204} {\it Note:} You must reboot your PC after installing the
-AdobePS driver for it to take effect.
-\item To produce the ps file, select ``Print'' from the MS app, choose
-the installed AdobePS printer, click on ``Properties'', click on ``Advanced.''
-\item Set ``TrueType Font'' to be ``Download as Softfont''
-\item Open the ``PostScript Options'' folder
-\item Select ``PostScript Output Option'' to be ``Optimize for Portability''
-\item Select ``TrueType Font Download Option'' to be ``Outline''
-\item Select ``Send PostScript Error Handler'' to be ``No''
-\item Click ``OK'' three times, print your file.
-\item Now, use Adobe Acrobat Distiller or ps2pdf to create a PDF file from
-the PS file. In Acrobat, check the option ``Embed all fonts'' if
-applicable.
-\end{itemize}
-
-\end{itemize}
-If your file contains Type 3 fonts or non embedded TrueType fonts, we will
-ask you to fix it.
-
-\subsection{Margins in LaTeX}
-
-Most of the margin problems come from figures positioned by hand using
-\verb+\special+ or other commands. We suggest using the command
-\verb+\includegraphics+
-from the graphicx package. Always specify the figure width as a multiple of
-the line width as in the example below using .eps graphics
-\begin{verbatim}
-   \usepackage[dvips]{graphicx} ... 
-   \includegraphics[width=0.8\linewidth]{myfile.eps} 
-\end{verbatim}
-or % Apr 2009 addition
-\begin{verbatim}
-   \usepackage[pdftex]{graphicx} ... 
-   \includegraphics[width=0.8\linewidth]{myfile.pdf} 
-\end{verbatim}
-for .pdf graphics. 
-See section 4.4 in the graphics bundle documentation (\url{http://www.ctan.org/tex-archive/macros/latex/required/graphics/grfguide.ps})
-
-A number of width problems arise when LaTeX cannot properly hyphenate a
-line. Please give LaTeX hyphenation hints using the \verb+\-+ command.
-
-\subsubsection*{Acknowledgments}
-
-Use unnumbered third level headings for the acknowledgments. All
-acknowledgments go at the end of the paper. Do not include 
-acknowledgments in the anonymized submission, only in the 
-final paper.
+\subsection{Results}
 
@@
 
-References follow the acknowledgments. Use unnumbered third level heading for
-the references. Any choice of citation style is acceptable as long as you are
-consistent. It is permissible to reduce the font size to `small' (9-point) 
-when listing the references. {\bf Remember that this year you can use
-a ninth page as long as it contains \emph{only} cited references.}
-
 \small{
-[1] Alexander, J.A. \& Mozer, M.C. (1995) Template-based algorithms
-for connectionist rule extraction. In G. Tesauro, D. S. Touretzky
-and T.K. Leen (eds.), {\it Advances in Neural Information Processing
-Systems 7}, pp. 609-616. Cambridge, MA: MIT Press.
-
-[2] Bower, J.M. \& Beeman, D. (1995) {\it The Book of GENESIS: Exploring
-Realistic Neural Models with the GEneral NEural SImulation System.}
-New York: TELOS/Springer-Verlag.
-
-[3] Hasselmo, M.E., Schnell, E. \& Barkai, E. (1995) Dynamics of learning
-and recall at excitatory recurrent synapses and cholinergic modulation
-in rat hippocampal region CA3. {\it Journal of Neuroscience}
-{\bf 15}(7):5249-5262.
+[1] Scikit-learn: Machine Learning in Python, Pedregosa et al., JMLR 12, pp. 2825-2830, 2011.
 }

### 2015-12-17 Writeup/submission_v01.tex
minor changes

@@
 
-% The \author macro works with any number of authors. There are two commands
-% used to separate the names and addresses of multiple authors: \And and \AND.
-%
-% Using \And between authors leaves it to \LaTeX{} to determine where to break
-% the lines. Using \AND forces a linebreak at that point. So, if \LaTeX{}
-% puts 3 of 4 authors names on the first line, and the last on the second
-% line, try using \AND instead of \And before the third author name.
-
 \newcommand{\fix}{\marginpar{FIX}}
@@
 \begin{abstract}
-abstract goes here
+abstract goes here TODO
+
 \end{abstract}
@@
 \section{Part 1}
-
 The goal of the project for part 1 is to classify subject behavior baed on raw voxel activation values.
@@
 The resulting accuracy was 60.47\% on the holdout data set.
+
 \subsection{SVM Classifier}
 Abhishek
+
 \subsection{Custom Feature Extraction}
-
 The custom feature extraction....
 
-\begin{figure}[h]
+\begin{figure}[H]
 \begin{center}
-%\framebox[4.0in]{$\;$}
-\includegraphics[scale=.5]{media/cross_validation_figure_2.png}
+\includegraphics[scale=.4]{media/pos_activation_formatted.png}
 \end{center}
@@
 
-\begin{table}[t]
+\begin{table}[H]
 \caption{Sample table title}
@@
 \subsection{MultiTaskLasso Cross Validation}
+
+MultiTask Lasso begin
+
+\begin{figure}[H]
+\begin{center}
+%\framebox[4.0in]{$\;$}
+\includegraphics[scale=.5]{media/cross_validation_figure_2.png}
+\end{center}
+\caption{Sample figure caption.}
+\end{figure}
+
+multitask lasso end
+
 \subsection{Euclidean Clustering}

### 2015-12-17 part3/part3.py
local changes

@@ -14,24 +14,6 @@ from sklearn import preprocessing
 from sklearn.feature_selection import SelectKBest
 from sklearn.pipeline import Pipeline, FeatureUnion
 import matplotlib.cm as cm
-#from sklearn.kernel_ridge import KernelRidge
-from sklearn.linear_model import Ridge, LogisticRegression, LinearRegression, Lasso
-
-''' Notes
-    1) Ridge alpha value has little to no effect on outcome
-    2) Kernel Ridge regression 
-        rbf, polynomial of higher degree, sigmoid kernels are garbage
-        
-    Results
-        PCA 50 -  Ridge score of 63.5
-        PCA 100 - Ridge score of 66.1 (rmse = .535688)
-        PCA 200 - Ridge score of 64.2
-              
-        PCA 50 -  Lasso score of 62.5
-        PCA 100 - Lasso score of 65
-    
-    
-end Notes'''
 
 file_loc = '/home/abhishekb/ML_Project2/data/'
 
@@ -60,56 +42,89 @@ X_train_raw = np.vstack((X_train_raw_1, X_train_raw_2))
 Y_train_raw = np.vstack((Y_train_raw_1, Y_train_raw_2))
 train_labels = np.vstack((import_test_labels['Ytest'],import_train['Ytrain'])) #labels of the original train data
 
+## Approach 2
 ## Standardization
 scaler = preprocessing.StandardScaler().fit(X_train_raw)
 X_train_scaled = scaler.transform(X_train_raw)
-X_test_scaled = scaler.transform(X_test_raw)
 
 ## PCA and Feature Selection
-
-'''pca = PCA(n_components=100)  
-pca.fit(X_train_scaled)
-#print(pca.explained_variance_ratio_) 
-X_train_reduced = pca.transform(X_train_scaled)
-X_test_reduced = pca.transform(X_test_scaled)
-'''
-
 pca = PCA(n_components=800)
 selection = SelectKBest(k=850)
 combined_features = FeatureUnion([("pca", pca), ("univ_select", selection)])
 combined_features.fit(X_train_scaled, train_labels.ravel())
-#print(pca.explained_variance_ratio_) 
 X_train_reduced = combined_features.transform(X_train_scaled)
-X_test_reduced = combined_features.transform(X_test_scaled)
 
[…]

### 2015-12-17 part3/project1template.py

@@ -15,7 +15,7 @@ from sklearn.feature_selection import SelectKBest
 from sklearn.pipeline import Pipeline, FeatureUnion
 import matplotlib.cm as cm
 
-file_loc = '/home/abhishekb/ML_Project2/data/'
+file_loc = '/home/apark/Homework/ML_Project2/data/'
 
 ## Import data
 import_test = sio.loadmat(file_loc + 'Test.mat')

### 2015-12-17 src/pca_svr.py

@@ -1,3 +1,9 @@
+"""
+Created on Tue Dec 15 12:09:50 2015
+
+@author: abhishekb
+"""
+
 # -*- coding: utf-8 -*-
 
 import numpy as np
@@ -16,12 +22,20 @@ from sklearn.pipeline import Pipeline, FeatureUnion
 import matplotlib.cm as cm
 #from sklearn.kernel_ridge import KernelRidge
 from sklearn.linear_model import Ridge, LogisticRegression, LinearRegression, Lasso
+from sklearn.svm import SVR, LinearSVR
 
 ''' Notes
-    1)
+    1) Ridge alpha value has little to no effect on outcome
+    2) Kernel Ridge regression 
+        rbf, polynomial of higher degree, sigmoid kernels are garbage
         
     Results
-    PCA 100, Kbest 50 - Ridge score of 66.1 
+        PCA 50 -  Ridge score of 63.5
+        PCA 100 - Ridge score of 66.1 (rmse = .535688)
+        PCA 200 - Ridge score of 64.2
+              
+        PCA 50 -  Lasso score of 62.5
+        PCA 100 - Lasso score of 65
     
     
 end Notes'''
@@ -35,16 +49,23 @@ import_providedidx = sio.loadmat(file_loc + 'provideIdx.mat')
 import_missidx = sio.loadmat(file_loc + 'missIdx.mat')
 import_providedata = sio.loadmat(file_loc + 'provideData_1000.mat')
 import_events = sio.loadmat(file_loc + 'events_1000.mat')
+import_test_labels = sio.loadmat(file_loc + 'Ytest.mat')
 
 provideIdx = import_providedidx['provideIdx'] - 1 # since Matlab indexing starts at 1
 provideIdx = provideIdx.ravel()
 missIdx = import_missidx['missIdx'] - 1 # since Matlab indexing starts at 1
 missIdx = missIdx.ravel()
 events = import_events['events']
+X_test_raw_1 = import_test['Xtest']
 X_test_raw = import_providedata['provideData'] # size = (1000, 3172)
 XY_train_raw = import_train['Xtrain']
-X_train_raw = XY_train_raw[:,provideIdx] # size = (500, 3172)
-Y_train_raw = XY_train_raw[:,missIdx] # size = (500, 2731)
[…]

### 2015-12-17 src/raw_ridge.py

@@ -14,7 +14,7 @@ from sklearn import preprocessing
 from sklearn.feature_selection import SelectKBest
 from sklearn.pipeline import Pipeline, FeatureUnion
 import matplotlib.cm as cm
-from sklearn.kernel_ridge import KernelRidge
+#from sklearn.kernel_ridge import KernelRidge
 from sklearn.linear_model import Ridge, LogisticRegression, LinearRegression, Lasso
 
 ''' Notes
@@ -27,7 +27,7 @@ from sklearn.linear_model import Ridge, LogisticRegression, LinearRegression, La
     
 end Notes'''
 
-file_loc = '/home/apark/Homework/ML_Project2/data/'
+file_loc = '/home/abhishekb/ML_Project2/data/'
 
 ## Import data
 import_test = sio.loadmat(file_loc + 'Test.mat')

### 2015-12-17 part3/part3.py
modified part3 (Working)

@@ -56,9 +56,11 @@ X_train_reduced = combined_features.transform(X_train_scaled)
 
 clf = Lasso(alpha=.01)
 clf.fit(X_train_reduced, Y_train_raw)
-Y_predicted = clf.predict(X_test_reduced)
+Y_predicted = clf.predict(X_train_reduced)
 
-X_train_raw_new = np.vstack((X_train_raw,Y_predicted)) 
+#Y_predicted = np.vstack(())
+
+X_train_raw_new = np.hstack((X_train_raw,Y_predicted)) 
 
 ## Standardization
 scaler = preprocessing.StandardScaler().fit(X_train_raw_new)

### 2015-12-18 Writeup/submission_v01.tex
local changes
added lastest changes to latex writeup

@@
 \section{Part 1}
-The goal of the project for part 1 is to classify subject behavior baed on raw voxel activation values.
-The final approach developed to achieve this goal includes an SVM classifier, custom feature extraction, and a voting method.
-The resulting accuracy was 60.47\% on the holdout data set.
+The goal of the project for part 1 is to classify subject behavior based on MRI voxel activation values.
+Data for voxel activation intensity, time the MRI machine was on, subject number, and relative geometric location was provided in the dataset.
+The three class labels reflected the subject response to the task of pressing a button when a moving progress bar reaches a line shown in Table 1.
+The final approach to classifying subject response based on the given data consists of a SVM classifier, custom feature classifiers, and a voting method.
 
-\subsection{SVM Classifier}
-Abhishek
-
-\subsection{Custom Feature Extraction}
-The custom feature extraction....
-
-\begin{figure}[H]
-\begin{center}
-\includegraphics[scale=.4]{media/pos_activation_formatted.png}
-\end{center}
-\caption{Sample figure caption.}
-\end{figure}
-
-\begin{table}[H]
-\caption{Sample table title}
-\label{sample-table}
+\begin{table}[h]
+\caption{Class Labels and Descriptions}
+\label{classtable}
 \begin{center}
 	\begin{tabular}{ll}
-\multicolumn{1}{c}{\bf HEADING C1}  &\multicolumn{1}{c}{\bf HEADING C2}
+		\multicolumn{1}{c}{\bf Class Label}  &\multicolumn{1}{c}{\bf Class Description}
 		\\ \hline \\
-r1c1   &r1c2       \\
-r2c1   &r2c2 \\
-etc		&etc\\
+		0) No Event   &       \\
+		1) Early Stop   &Successful stop to and early stop signal \\
+		3) Correct Go		&Correct button press within 500 ms on a trial with no stop signal\\
 	\end{tabular}
@@
 
+\subsection{SVM Classifier}
+The Support Vector Machine (SVM) is a very popular and useful technique used for data classification.
+But even before beginning with the statistical machine learning techniques, data processing techniques were applied to convert the raw data into suitable form to extract the useful information.
+We started with standardization of the data for mean removal and variance scaling.
+This is necessary because the machine learning estimators used might give unexpected results if the data is not in standard, normally distributed form [1].
+Other scaling methods were attempted to scale features not across zero mean, but across certain ranges, but ultimately these approaches were inferior to the first standardization method discussed above.
+Besides scaling, attempts to normalizing individual samples to have unit norm did not improve classifier performance.
+After standardization, feature selection and dimensionality reduction techniques were applied to reduce the number of features and only consider important features for classification.
+Principal Component Analysis (PCA) is a linear dimensionality reduction technique that that uses singular value decomposition of the data and keeps only the most significant singular vectors to project the data to a lower dimension space[2].
+Along with PCA,the Univariate Feature Selection method was used for selecting the best features based on univariate statistical tests.
+The combination of these two methods combine to form the preprocessing step for our estimator[3].The select\_k\_best function was invoked for our feature selection that removes all but k highest scoring features.
+Finally, SVM was used as the supervised learning method for classification.
+The SVM was selected because of various reasons such as effectiveness with high dimension cases, effective especially in cases where number of features are more than the number of samples, and versatility meaning different kernels can be specified as the decision function[4].
+To do the comparison, three different SVM classifiers were evaluated, linear SVM, polynomial SVM and radial basis function (RBF) kernel SVM.
+Furthermore, cross validation techniques to used to fine tune the parameters and evaluate the overall performance of the pipeline.
+Ten fold cross validation methods helped avoid overfitting and achieved the best accuracy.
+Below are the final parameters that gave us the best accuracy:
+PCA components = 800
+Univariate Feature Selection (K-best components) = 450
+Linear SVM, C = 10
+Polynomial SVM, C = 1, degree = 3
+RBF kernel SVM, C = 10, gamma = 0.0001
+
+\subsection{Custom Feature Extraction}
+Since the voxel intensities can be thought to reflect cognitive function and internal feedback, a classifier was sought to that would be able to map the three responses to unique spacial locations in the brain.
+The voxel data was segmented by class and statistical measures were taken from each segmentation.
+The data was thresholded by high  and low activation relative to standard deviation and mean of each voxel and visualized to determine if there was evidence these features could serve as good classifiers.
+Figure 1 shows a geometric representation of the positive activations of each class thresholded by these statistical measures.
+
+\begin{figure}[h]
+	\begin{center}
+		\includegraphics[scale=.35]{media/pos_4x4_formatted.png}
+	\end{center}
+	\caption{Relative Geometric Locations of Postive Voxel Activations by Class Label}
+\end{figure}
+
+These visualizations show that distinct spatial areas of the brain seem to activate or go inactive when they showed different responses.
+The features and other similar measures were combined into a truth matrix.
+The truth matrix was used to transform the 5903 voxel features space into a six feature space, 3 features for low activation per class and 3 for high activations per class.
+This same approach was applied to the data after being reduced through Principal Component Analysis which converted the 5903 voxel features to just 100 features.
+A binary truth matrix was generated which looked at features where the mean was strongly positive or strongly negative for each class.
+The 100 PCA features were transformed into just 6 features.
+For each six feature feature space, at Gaussian Naive Bayes classifier was used to train the data on the provided training set and used to predict the labels of the test set.
+Independently, these classifiers did not outperform the SVM classifier.
+
 \subsection{Voting Method}
+A voting methodology was sought to combine the strengths of the SVM classifier and the 2 custom feature Gaussian Naive Bayes classifiers.
+Several voting methods were tested but the best results were obtained by equally weighting each classifier so that if any two agreed on a class label that became the predicted class label.
+Any three-way tie was broken by assigning class 3 which was the most dense class in the dataset and is statistically the best guess.
+\subsection{Results}
+
+Table 2 shows the accuracies achieved on the 10-fold cross validation of the training data, for two SVM based classifiers described above in addition to the final voting ensemble.
+
+\begin{table}[h]
+\caption{Cross Validation Accuracy for Part 1}
+\label{classtable}
+\begin{center}
+	\begin{tabular}{llll}
+		\multicolumn{1}{c}{\bf Fold}  &\multicolumn{1}{c}{\bf Voting} &\multicolumn{1}{c}{\bf RBF SVM} &\multicolumn{1}{c}{\bf Linear SVM}
+		\\ \hline \\
+		Fold 1   &0.6923 &0.6275 &0.5882\\
+		Fold 2   &0.5769 &0.68 &0.56\\
+		Fold 3   &0.6471 &0.62 &0.52\\
+		Fold 4   &0.64   &0.52 &0.42\\
+		Fold 5   &0.78   &0.64 &0.48\\
+		Fold 6   &0.70   &0.66 &0.60\\
+		Fold 7   &0.6531 &0.60 &0.48\\
+		Fold 8   &0.6122 &0.70 &0.62\\
+		Fold 9   &0.5510 &0.74 &0.62\\
+		Fold 10   &0.6939 &0.66 &0.54\\
+		Average Accuracy   &0.6505 &0.6467 &0.5378\\
+	\end{tabular}
+\end{center}
+\end{table}
+
+The resulting total accuracy that was achieved on 1000 test data points was 63.1\%.
 
 \section{Part 2}
+The goal of project part 2 is to predict the remaining voxel values from the partial fMRI image dataset provided
+
+\subsection{Clustering}
+Geometric clustering could be a way to encode domain knowledge into the classification.
+The rationale is that missing voxels should have similar intensities to other known voxels in the local region in the brain.
+An algorithm resembling k nearest neighbors was developed to find which known voxels were in the neighborhood of missing voxels.
+Statistical measures were taken of each missing feature and on each sample.
+The standard deviation is a good measure at the uniformity of each missing voxel for each brain scan.
+If the standard deviation was below some threshold, the missing voxel took on the median or mean of the local known voxels otherwise the missing voxel would take a predicted value from regression.
+Different k values were attempted along with different standard deviation thresholds to attempt to improve performance.
+It was discovered this method could improve a poor regression model but after the regression model was better than .55 root mean square error this method only degraded performance.
+
 \subsection{Ridge and Lasso Classifiers}
+For this, we started with similar data processing techniques, as described in project part 1.
+We first standardized the data to have a normal distribution and then applied a PCA and Univariate Feature Selection feature selection techniques to reduce and select the best features.
+Further, we used regression to predict the remaining voxel values and used cross validation to compare scores and ensure we were not overfitting.
+We used various techniques from the Generalized linear models that are intended for regression where target values are expected to be a linear combination of input values.
+We tried linear regression, ridge regression and finally settled with lasso regression with a value of the regularization parameter alpha = .01, that gave us the minimum root mean square error for the predicted voxel values.
+
 \subsection{MultiTaskLasso Cross Validation}
+After performing PCA, a cross validation parameter sweep was performed from the sklearn api using MultiTaskLassoCV.
+This function sweeps across the alpha values that penalize the cost function the Lasso model seeks to minimize.
+The initial run showed cross validation mean squared error to decrease with alpha.
+Another run was performed on even smaller alphas looking for the global minimum.
+Figure 2 shows the resulting cross validation error for different alpha values between 0.1 and 1.0.
 
-MultiTask Lasso begin
-
-\begin{figure}[H]
+\begin{figure}[h]
 	\begin{center}
-%\framebox[4.0in]{$\;$}
-\includegraphics[scale=.5]{media/cross_validation_figure_2.png}
+		\includegraphics[scale=.4]{media/cross_validation_figure_2.png}
 	\end{center}
-\caption{Sample figure caption.}
+	\caption{mean Square Error from Cross Validation}
 \end{figure}
 
-multitask lasso end
+The optimization shows the global minimum of mean square error occurs at an alpha value of approximately 0.4.
+A 10 fold cross validation analysis with finer alpha internal resolution placed the mean square error minimum closer to an alpha of 0.3 This was the final selected classifier used for part 2 assignment submission.
 
-\subsection{Euclidean Clustering}
+\subsection{Results}
+text
+
+text
+
+text
+
+\begin{table}[h]
+\caption{Cross Validation Accuracy for Part 2}
+\label{classtable}
+\begin{center}
+	\begin{tabular}{ll}
+		\multicolumn{1}{c}{\bf Fold}  &\multicolumn{1}{c}{\bf MultiTaskLasso Accuracy} 
+		\\ \hline \\
+		Fold 1   &0.5682 \\
+		Fold 2   &0.5478 \\
+		Fold 3   &0.4765 \\
+		Fold 4   &0.5007   \\
+		Fold 5   &0.5414   \\
+		Fold 6   &0.5126   \\
+		Fold 7   &0.5961 \\
+		Fold 8   &0.5238 \\
+		Fold 9   &0.5832 \\
+		Fold 10   &0.5333 \\
+		Average Accuracy   &0.5384\\
+	\end{tabular}
+\end{center}
+\end{table}
+
+The final root mean square error achieved on the holdout set was 0.4693
 
@@
 \subsection{Hypothesis}
+Given the a full test set of 1000 samples with full voxel values and class assignments, the hypothesis tested for part three is to evaluate the which classification would perform better directly predicting class labels from the provided voxel subset denoted ‘Direct’ in Figure 3,  or predict the missing voxels and then predict the class labels from the reconstructed full voxel set denoted ‘Indirect’ ’in Figure 3.
+The Direct approach is straightforward and does not attempt to waste any information learning the full brain model but will suffer from the smaller set of features to train and test on.
+The Indirect approach may use a priori knowledge of the brain model to enhance the feature space but may perform poorly if the accuracy of the voxel reconstruction is poor.
+
+\begin{figure}[h]
+	\begin{center}
+		\includegraphics[scale=.35]{media/take2.png}
+	\end{center}
+	\caption{Direct and Indirect Methods for Class Estimation}
+\end{figure}
 
 \subsection{Experiment}
+To test the Direct and Indirect methods of class prediction from the provided voxel set, the input data was first split between provided and missing voxel features where the missing voxels were discarded.
+The provided class labels were retained to allow for accurate measures of cross validation.
+For the Direct approach, the same feature selection method, PCA with 800 components and univariate selection with 450 components, was used as in part 1 but operated only on the provided voxels.
+The SVM classifier was retained but the custom feature classifier were omitted since they may have operated on voxel values that are now missing.
+For the Indirect approach, the exact same classifier used in part 1 and part 2 were used.
+After missing voxel reconstruction, the predicted voxels were simply appended to the original voxels and then the classifier for part 1 predicted features from this mixture set.
 
 \subsection{Results}
+text
+
+text
+
+text
+
+text
+
+text
+
+text
+
+text
+
+text
+
+text
+
+\begin{table}[h]
+\caption{Cross Validation Accuracy for Part 3}
+\label{classtable}
+\begin{center}
+	\begin{tabular}{lll}
+		\multicolumn{1}{c}{\bf Fold}  &\multicolumn{1}{c}{\bf Accuracy of Direct Approach} &\multicolumn{1}{c}{\bf Accuracy of Indirect Approach} 
+		\\ \hline \\
+		Fold 1   &0.5714 &0.5648 \\
+		Fold 2   &0.5914 &0.5714 \\
+		Fold 3   &0.61 &0.59 \\
+		Fold 4   &0.61   &0.61 \\
+		Fold 5   &0.5933   &0.5767 \\
+		Average Accuracy   &0.5952 &0.5826\\
+	\end{tabular}
+\end{center}
+\end{table}
+
+FINAL RESULT
 
@@
 \small{
-[1] Scikit-learn: Machine Learning in Python, Pedregosa et al., JMLR 12, pp. 2825-2830, 2011.
+[1] http://scikit-learn.org/stable/modules/preprocessing.html
+
+[2] http://scikit-learn.org/stable/modules/generated/sklearn.decomposition.PCA.html
+
+[3] http://scikit-learn.org/stable/modules/feature\_selection.html
+
+[4] http://scikit-learn.org/stable/modules/svm.html
+
+[5] http://scikit-learn.org/stable/modules/linear\_model.html
+
+[x]Scikit-learn: Machine Learning in Python, Pedregosa et al., JMLR 12, pp. 2825-2830, 2011.
+
 }

### 2015-12-18 src/pc_multiclassLasso.py

@@ -70,30 +70,30 @@ X_train_reduced = combined_features.transform(X_train_scaled)
 X_test_reduced = combined_features.transform(X_test_scaled)
 
 ## Create K folds
-k_fold = KFold(Y_train_raw.shape[0], n_folds=4)
-for train, test in k_fold:
-    X1 = X_train_reduced[train]
-    Y1 = Y_train_raw[train]
-    
-    X2 = X_train_reduced[test]
-    Y2 = Y_train_raw[test]    
-
-    ## Train Classifiers on fold
-    mcl_clf = MultiTaskLasso(alpha=.6257)
-    mcl_clf.fit(X1, Y1)
-
-
-    ## Score Classifiers on fold
-
-    mcl_clf_score = mcl_clf.score(X2, Y2)
-
-    print "MultiTaskLasso:  ", mcl_clf_score
+#k_fold = KFold(Y_train_raw.shape[0], n_folds=4)
+#for train, test in k_fold:
+#    X1 = X_train_reduced[train]
+#    Y1 = Y_train_raw[train]
+#    
+#    X2 = X_train_reduced[test]
+#    Y2 = Y_train_raw[test]    
+#
+#    ## Train Classifiers on fold
+#    mcl_clf = MultiTaskLasso(alpha=.6257)
+#    mcl_clf.fit(X1, Y1)
+#
+#
+#    ## Score Classifiers on fold
+#
+#    mcl_clf_score = mcl_clf.score(X2, Y2)
+#
+#    print "MultiTaskLasso:  ", mcl_clf_score
 
 
 
 ## Lasso CV for parameter optimization
 t1 = time.time()
-clf = MultiTaskLasso(alpha=.6257).fit(X_train_reduced, Y_train_raw)
+clf = MultiTaskLasso(alpha=.3).fit(X_train_reduced, Y_train_raw)
 t_lasso_cv = time.time() - t1
 print 'time to train', t_lasso_cv
 

### 2015-12-18 part3/part3_reconstruction.py
added reconstruction file to part3

@@ -1,0 +1,147 @@
+# -*- coding: utf-8 -*-
+
+import numpy as np
+import scipy.io as sio
+import matplotlib.pyplot as plt
+import numpy as np
+from sklearn.cross_validation import KFold
+from sklearn import svm
+from sklearn.feature_selection import SelectKBest
+from sklearn.decomposition import PCA
+from sklearn import cross_validation
+from sklearn.cross_validation import StratifiedKFold
+from sklearn import preprocessing
+from sklearn.feature_selection import SelectKBest
+from sklearn.pipeline import Pipeline, FeatureUnion
+from sklearn.linear_model import MultiTaskLasso
+from sklearn.metrics import accuracy_score
+import matplotlib.cm as cm
+
+#file_loc = '/home/abhishekb/ML_Project2/data/'
+file_loc = '/home/apark/Homework/ML_Project2/data/'
+## Import data
+import_test = sio.loadmat(file_loc + 'Test.mat')
+import_train = sio.loadmat(file_loc + 'Train.mat')
+import_providedidx = sio.loadmat(file_loc + 'provideIdx.mat')
+import_missidx = sio.loadmat(file_loc + 'missIdx.mat')
+import_providedata = sio.loadmat(file_loc + 'provideData_1000.mat')
+import_events = sio.loadmat(file_loc + 'events_1000.mat')
+import_test_labels = sio.loadmat(file_loc + 'Ytest.mat')
+
+provideIdx = import_providedidx['provideIdx'] - 1 # since Matlab indexing starts at 1
+provideIdx = provideIdx.ravel()
+missIdx = import_missidx['missIdx'] - 1 # since Matlab indexing starts at 1
+missIdx = missIdx.ravel()
+events = import_events['events']
+X_test_raw_1 = import_test['Xtest']
+X_test_raw = import_providedata['provideData'] # size = (1000, 3172)
+XY_train_raw = import_train['Xtrain']
+X_train_raw_2 = XY_train_raw[:,provideIdx] # size = (500, 3172)
+X_train_raw_1 = X_test_raw_1[:,provideIdx]  
+Y_train_raw_2 = XY_train_raw[:,missIdx] # size = (500, 2731)
+Y_train_raw_1 = X_test_raw_1[:,missIdx]
+X_train_raw = np.vstack((X_train_raw_1, X_train_raw_2))
+Y_train_raw = np.vstack((Y_train_raw_1, Y_train_raw_2))
[…]

### 2015-12-18 part3/part3.py
Updated part3.py

@@ -14,6 +14,8 @@ from sklearn import preprocessing
 from sklearn.feature_selection import SelectKBest
 from sklearn.pipeline import Pipeline, FeatureUnion
 import matplotlib.cm as cm
+from sklearn.linear_model import Ridge, LogisticRegression, LinearRegression, Lasso
+
 
 file_loc = '/home/abhishekb/ML_Project2/data/'
 

### 2015-12-18 part3/part3_reconstruction.py
latest changes to reconstruction for part 3

@@ -15,6 +15,7 @@ from sklearn.feature_selection import SelectKBest
 from sklearn.pipeline import Pipeline, FeatureUnion
 from sklearn.linear_model import MultiTaskLasso
 from sklearn.metrics import accuracy_score
+from sklearn.metrics import mean_squared_error
 import matplotlib.cm as cm
 
 #file_loc = '/home/abhishekb/ML_Project2/data/'
@@ -60,10 +61,9 @@ clf = MultiTaskLasso(alpha=.3)
 clf.fit(X_train_reduced, Y_train_raw)
 Y_predicted = clf.predict(X_train_reduced)
 
-interval = np.linspace(0,1500,15)
-for iteration in range(interval):
+
     #Y_predicted = np.vstack(())
-    replacement_mod = interval[iteration]; # 1500-perfect 0-predicted
+    replacement_mod = iteration; # 1500-perfect 0-predicted
     print 'replacement_mod', replacement_mod
     Y_reconstruction = Y_train_raw
     for i in range(0,Y_train_raw.shape[0]):
@@ -71,7 +71,7 @@ for iteration in range(interval):
             print i
             Y_reconstruction[i,:] = Y_predicted[i,:] 
             
-    recon_acc = accuracy_score(Y_train_raw, Y_reconstruction)
+    recon_acc = mean_squared_error(Y_train_raw, Y_reconstruction)
     print 'reconstruction accuracy:', recon_acc
     
     

### 2015-12-18 part3/part3_reconstruction.py
including for loop to reconstruction

@@ -61,7 +61,8 @@ clf = MultiTaskLasso(alpha=.3)
 clf.fit(X_train_reduced, Y_train_raw)
 Y_predicted = clf.predict(X_train_reduced)
 
-
+interval = [1,2,3,4,5,6,10,50,500]
+for iteration in interval:
     #Y_predicted = np.vstack(())
     replacement_mod = iteration; # 1500-perfect 0-predicted
     print 'replacement_mod', replacement_mod

### 2015-12-18 Writeup/submission_v01.tex
added to latex writeup, formatting and content revisions

@@
 \usepackage{graphicx}
+\usepackage{wrapfig}
 %\documentstyle[nips14submit_09,times,art10]{article} % For LaTeX 2.09
@@
 \begin{abstract}
-abstract goes here TODO
+MRI data was captured and labelled for analysis to understand the relationship between 5903 brain voxel values and subject behavior to a time-based task.
+Part one aims to make a classifier capable of predicting the class label based on a full set of brain voxels.
+The best approach was to create a voting ensemble between and SVM classifier and two sets of extracted features from domain knowledge coupled with Gaussian naive Bayes classifiers resulting in a prediction accuracy of 63.1\%.
+Part 2 aims to reconstruct missing voxel intensities from a subset of the full voxel set.
+The best approach resulted in a root mean square error of .4693 and accomplished this by performing feature selection on the provided voxels and predicting the missing voxels with MultiTaskLasso regression provided by the sklearn API [1].
+Part three explains an experiment to classify labels based on the provided voxel subset using direct and indirect estimation methods.
+The results of the experiment show that directly learning the class label from the provided voxels performed better than indirect learning methods.
 
@@
 Besides scaling, attempts to normalizing individual samples to have unit norm did not improve classifier performance.
+
 After standardization, feature selection and dimensionality reduction techniques were applied to reduce the number of features and only consider important features for classification.
@@
 The combination of these two methods combine to form the preprocessing step for our estimator[3].The select\_k\_best function was invoked for our feature selection that removes all but k highest scoring features.
+
 Finally, SVM was used as the supervised learning method for classification.
@@
 \subsection{Custom Feature Extraction}
+
+\begin{wrapfigure}{r}{0.5\textwidth}
+	\begin{center}
+		\includegraphics[scale=.25]{media/pos_4x4_formatted.png}
+	\end{center}
+	\caption{Relative Geometric Locations of Postive Voxel Activations by Class Label}
+	\vspace{-20pt}
+\end{wrapfigure}
+
 Since the voxel intensities can be thought to reflect cognitive function and internal feedback, a classifier was sought to that would be able to map the three responses to unique spacial locations in the brain.
@@
 Figure 1 shows a geometric representation of the positive activations of each class thresholded by these statistical measures.
-
-\begin{figure}[h]
-	\begin{center}
-		\includegraphics[scale=.35]{media/pos_4x4_formatted.png}
-	\end{center}
-	\caption{Relative Geometric Locations of Postive Voxel Activations by Class Label}
-\end{figure}
 
@@
 Geometric clustering could be a way to encode domain knowledge into the classification.
-The rationale is that missing voxels should have similar intensities to other known voxels in the local region in the brain.
+The rationale is that missing voxels should have similar intensities to other known voxels in the local subregions in the brain.
 An algorithm resembling k nearest neighbors was developed to find which known voxels were in the neighborhood of missing voxels.
-Statistical measures were taken of each missing feature and on each sample.
+Statistical measures were taken of each subregion for each sample and for each missing voxel.
 The standard deviation is a good measure at the uniformity of each missing voxel for each brain scan.
@@
 Different k values were attempted along with different standard deviation thresholds to attempt to improve performance.
-It was discovered this method could improve a poor regression model but after the regression model was better than .55 root mean square error this method only degraded performance.
+It was discovered this method could improve a poor regression model but after the regression model was better than .55 root mean square error this method only degraded performance and was abandoned.
 
-\subsection{Ridge and Lasso Classifiers}
-For this, we started with similar data processing techniques, as described in project part 1.
-We first standardized the data to have a normal distribution and then applied a PCA and Univariate Feature Selection feature selection techniques to reduce and select the best features.
-Further, we used regression to predict the remaining voxel values and used cross validation to compare scores and ensure we were not overfitting.
-We used various techniques from the Generalized linear models that are intended for regression where target values are expected to be a linear combination of input values.
-We tried linear regression, ridge regression and finally settled with lasso regression with a value of the regularization parameter alpha = .01, that gave us the minimum root mean square error for the predicted voxel values.
+\subsection{Regression Classifiers}
+
+To perform regression, similar data processing techniques were used, as described in Section 1.1.
+The input data was standardized to have a normal distribution and then PCA was applied along and Univariate Feature Selection feature selection techniques to reduce and select the best features.
+
+Several regression models were used to predict the remaining voxel values.
+Ten fold cross validation was used to compare scores and ensure the model did not over fit the data.
+Various techniques from the Generalized linear models were attempted such as Ridge regression and Lasso regression with L1 and L2 penalties.
+These regression models are intended for regression where target values are expected to be a linear combination of input values.
+After comparing the regression models, the lasso regression model appeared to be best suited for this task.
 
 \subsection{MultiTaskLasso Cross Validation}
-After performing PCA, a cross validation parameter sweep was performed from the sklearn api using MultiTaskLassoCV.
+
+\begin{wrapfigure}{r}{0.5\textwidth}
+	\vspace{-20pt}
+	\begin{center}
+		\includegraphics[scale=.35]{media/cross_validation_figure_2.png}
+	\end{center}
+	\caption{MulitTaskLasso Mean Square Error from Cross Validation}
+	\vspace{-20pt}
+\end{wrapfigure}
+
+After performing PCA, a cross validation parameter sweep was performed from the sklearn api using MultiTaskLassoCV[X].
 This function sweeps across the alpha values that penalize the cost function the Lasso model seeks to minimize.
 The initial run showed cross validation mean squared error to decrease with alpha.
-Another run was performed on even smaller alphas looking for the global minimum.
+Another run was performed on even smaller alpha values looking for the global minimum.
 Figure 2 shows the resulting cross validation error for different alpha values between 0.1 and 1.0.
 
-\begin{figure}[h]
-	\begin{center}
-		\includegraphics[scale=.4]{media/cross_validation_figure_2.png}
-	\end{center}
-	\caption{mean Square Error from Cross Validation}
-\end{figure}
-
 The optimization shows the global minimum of mean square error occurs at an alpha value of approximately 0.4.
-A 10 fold cross validation analysis with finer alpha internal resolution placed the mean square error minimum closer to an alpha of 0.3 This was the final selected classifier used for part 2 assignment submission.
+A 10 fold cross validation analysis with finer alpha resolution placed the mean square error minimum closer to an alpha of 0.3 This was the final selected classifier used for part 2 assignment submission.
 
@@
 	\begin{tabular}{ll}
-		\multicolumn{1}{c}{\bf Fold}  &\multicolumn{1}{c}{\bf MultiTaskLasso Accuracy} 
+		\multicolumn{1}{c}{\bf Fold}  &\multicolumn{1}{c}{\bf MultiTaskLasso Accuracy (alpha = .3)} 
 		\\ \hline \\
@@
 
-\begin{figure}[h]
+\begin{wrapfigure}{r}{0.5\textwidth}
 	\begin{center}
@@
 	\caption{Direct and Indirect Methods for Class Estimation}
-\end{figure}
+	\vspace{-20pt}
+\end{wrapfigure}
 

### 2015-12-19 Writeup/submission_v01.tex
final report submission_v2!

@@
 Part one aims to make a classifier capable of predicting the class label based on a full set of brain voxels.
-The best approach was to create a voting ensemble between and SVM classifier and two sets of extracted features from domain knowledge coupled with Gaussian naive Bayes classifiers resulting in a prediction accuracy of 63.1\%.
+The best approach was to create a voting ensemble between a SVM classifier and two sets of extracted features from domain knowledge coupled with Gaussian naive Bayes classifiers resulting in a prediction accuracy of 63.1\%.
 Part 2 aims to reconstruct missing voxel intensities from a subset of the full voxel set.
-The best approach resulted in a root mean square error of .4693 and accomplished this by performing feature selection on the provided voxels and predicting the missing voxels with MultiTaskLasso regression provided by the sklearn API [1].
+The best approach resulted in a root mean square error of .4693 and accomplished this by performing feature selection on the provided voxels and predicting the missing voxels with MultiTaskLasso regression provided by the Scikit-learn API [1].
 Part three explains an experiment to classify labels based on the provided voxel subset using direct and indirect estimation methods.
-The results of the experiment show that directly learning the class label from the provided voxels performed better than indirect learning methods.
+The results of the experiment show that directly learning the class label from the provided voxels performed better than indirect learning methods for the given samples and achieved accuracies by each classification.
 
@@
 We started with standardization of the data for mean removal and variance scaling.
-This is necessary because the machine learning estimators used might give unexpected results if the data is not in standard, normally distributed form [1].
+This is necessary because the machine learning estimators used might give unexpected results if the data is not in standard, normally distributed form [2].
 Other scaling methods were attempted to scale features not across zero mean, but across certain ranges, but ultimately these approaches were inferior to the first standardization method discussed above.
@@
 After standardization, feature selection and dimensionality reduction techniques were applied to reduce the number of features and only consider important features for classification.
-Principal Component Analysis (PCA) is a linear dimensionality reduction technique that that uses singular value decomposition of the data and keeps only the most significant singular vectors to project the data to a lower dimension space[2].
+Principal Component Analysis (PCA) is a linear dimensionality reduction technique that that uses singular value decomposition of the data and keeps only the most significant singular vectors to project the data to a lower dimension space[3].
 Along with PCA,the Univariate Feature Selection method was used for selecting the best features based on univariate statistical tests.
-The combination of these two methods combine to form the preprocessing step for our estimator[3].The select\_k\_best function was invoked for our feature selection that removes all but k highest scoring features.
+The combination of these two methods combine to form the preprocessing step for our estimator[4].The select\_k\_best function was invoked for our feature selection that removes all but k highest scoring features.
 
 Finally, SVM was used as the supervised learning method for classification.
-The SVM was selected because of various reasons such as effectiveness with high dimension cases, effective especially in cases where number of features are more than the number of samples, and versatility meaning different kernels can be specified as the decision function[4].
+The SVM was selected because of various reasons such as effectiveness with high dimension cases, effective especially in cases where number of features are more than the number of samples, and versatility meaning different kernels can be specified as the decision function[5].
 To do the comparison, three different SVM classifiers were evaluated, linear SVM, polynomial SVM and radial basis function (RBF) kernel SVM.
@@
 
-The resulting total accuracy that was achieved on 1000 test data points was 63.1\%.
+The resulting total accuracy that was achieved on the set of 1000 test data points was 63.1\%.
 
 \section{Part 2}
-The goal of project part 2 is to predict the remaining voxel values from the partial fMRI image dataset provided
+The goal of project part 2 is to reconstruct the intensity values for a set of missing voxels given a subset of the original 5903 voxels in the fMRI brain scan.
+The missing voxels set consists of 2731 voxels and the provided voxel set consists of 3172 voxels of the original 5903 voxels.
+The missing voxel set is large relative to the provided feature set which will certainly limit the best possible accuracy however with sufficient data of the brain it should be possible to train a model to predict the missing voxels with acceptable error.
+To validate this data, the root mean square error will be used.
 
@@
 The standard deviation is a good measure at the uniformity of each missing voxel for each brain scan.
-If the standard deviation was below some threshold, the missing voxel took on the median or mean of the local known voxels otherwise the missing voxel would take a predicted value from regression.
+If the standard deviation was below some threshold, the missing voxel took on the mean of the local known voxels otherwise the missing voxel would take a predicted value from regression.
 Different k values were attempted along with different standard deviation thresholds to attempt to improve performance.
@@
 
-To perform regression, similar data processing techniques were used, as described in Section 1.1.
+To perform regression, similar data processing techniques were used as in Section 1.1.
 The input data was standardized to have a normal distribution and then PCA was applied along and Univariate Feature Selection feature selection techniques to reduce and select the best features.
@@
 Ten fold cross validation was used to compare scores and ensure the model did not over fit the data.
-Various techniques from the Generalized linear models were attempted such as Ridge regression and Lasso regression with L1 and L2 penalties.
+Various techniques from the Generalized linear models were attempted such as Ridge regression and Lasso regression with L1 and L2 penalties[6].
 These regression models are intended for regression where target values are expected to be a linear combination of input values.
 After comparing the regression models, the lasso regression model appeared to be best suited for this task.
+Sweeping the lasso alpha value across a range of alpha values, indicated that small values of alpha resulted in better prediction accuracy.
+However, the time to train and predict from models with small alphas less than .1 increased run time from seconds to hours.
+A lasso alpha value of .05 was selected for its tradeoff with runtime and accuracy, shown in Table 3.
 
@@
 
-After performing PCA, a cross validation parameter sweep was performed from the sklearn api using MultiTaskLassoCV[X].
-This function sweeps across the alpha values that penalize the cost function the Lasso model seeks to minimize.
+A cross validation parameter sweep was performed from the Scikit-learn API using MultiTaskLassoCV[7].
+This function sweeps across the alpha values that penalize the cost function the Lasso model seeks to minimize using coordinate descent.
 The initial run showed cross validation mean squared error to decrease with alpha.
@@
 Figure 2 shows the resulting cross validation error for different alpha values between 0.1 and 1.0.
+Like with the runtime on the Lasso classifier, the runtime for MulitTaskLassoCV increased with decreasing alpha value.
 
 The optimization shows the global minimum of mean square error occurs at an alpha value of approximately 0.4.
-A 10 fold cross validation analysis with finer alpha resolution placed the mean square error minimum closer to an alpha of 0.3 This was the final selected classifier used for part 2 assignment submission.
+A 10 fold cross validation analysis with finer alpha resolution placed the mean square error minimum closer to an alpha of 0.3.
+The result of the 10 fold cross validation is shown in Table 3.
 
 \subsection{Results}
-text
-
-text
-
-text
 
@@
 \begin{center}
-	\begin{tabular}{ll}
-		\multicolumn{1}{c}{\bf Fold}  &\multicolumn{1}{c}{\bf MultiTaskLasso Accuracy (alpha = .3)} 
+	\begin{tabular}{lll}
+		\multicolumn{1}{c}{\bf Fold}   &\multicolumn{1}{c}{\bf Lasso Accuracy (alpha = .05)} &\multicolumn{1}{c}{\bf MultiTaskLasso Accuracy (alpha = .3)}
 		\\ \hline \\
-		Fold 1   &0.5682 \\
-		Fold 2   &0.5478 \\
-		Fold 3   &0.4765 \\
-		Fold 4   &0.5007   \\
-		Fold 5   &0.5414   \\
-		Fold 6   &0.5126   \\
-		Fold 7   &0.5961 \\
-		Fold 8   &0.5238 \\
-		Fold 9   &0.5832 \\
-		Fold 10   &0.5333 \\
-		Average Accuracy   &0.5384\\
+		Fold 1   &0.5682 &0.5723\\
+		Fold 2   &0.5478 &0.5504\\
+		Fold 3   &0.4765 &0.4844\\
+		Fold 4   &0.5007 &0.5059  \\
+		Fold 5   &0.5414 &0.5449  \\
+		Fold 6   &0.5126 &0.517  \\
+		Fold 7   &0.5961 &0.6011\\
+		Fold 8   &0.5238 &0.5282\\
+		Fold 9   &0.5832 &0.5875\\
+		Fold 10   &0.5333 &0.5393 \\
+		Average Accuracy   &0.5384 & 0.5431\\
 	\end{tabular}
@@
 
+The cross validation results for both the Scikit-learn Lasso and MultiTaskLasso transformers are shown in Table 2.
+The accuracy for both of these methods is similar which reaffirms these tuned classifiers are not overfitting the data.
+Since the MultiTaskLassoCV corroborates these models, the final classifier used was the MultiTaskLasso with an alpha of .03.
 The final root mean square error achieved on the holdout set was 0.4693
@@
 \subsection{Hypothesis}
-Given the a full test set of 1000 samples with full voxel values and class assignments, the hypothesis tested for part three is to evaluate the which classification would perform better directly predicting class labels from the provided voxel subset denoted ‘Direct’ in Figure 3,  or predict the missing voxels and then predict the class labels from the reconstructed full voxel set denoted ‘Indirect’ ’in Figure 3.
-The Direct approach is straightforward and does not attempt to waste any information learning the full brain model but will suffer from the smaller set of features to train and test on.
-The Indirect approach may use a priori knowledge of the brain model to enhance the feature space but may perform poorly if the accuracy of the voxel reconstruction is poor.
+Given the a full test set of 1500 samples with full voxel values and class assignments, the hypothesis to be tested for part three is to evaluate the which classification would perform better directly predicting class labels from the provided voxel subset denoted ‘Direct’ in Figure 3,  or predict the missing voxels first and then predict the class labels from the reconstructed full voxel set denoted ‘Indirect’ in Figure 3.
+The Direct approach is straightforward and does not attempt to waste any information learning the full brain model but will suffer from the smaller set of features on which to train and test.
+The Indirect approach may use a priori knowledge of the brain model to enhance the feature space but may perform poorly if the accuracy of the voxel reconstruction is too inaccurate.
 
@@
 \subsection{Results}
-text
 
-text
+Below are the results for the two approaches described above (Direct and Indirect approach) on a five fold cross-validation experiment and also the accuracies achieved on the complete dataset (1500 X 5903).
 
-text
-
-text
-
-text
-
-text
-
-text
-
-text
-
-text
+From the results, it can be deduced that the Direct approach is a better for the cases where the reconstruction error in generating the missing dataset during the Indirect approach is large, as we can achieve better accuracy with the smaller dataset and at the same time, not waste our resources in first regeneration and then classification.
+However, if the reconstruction error in generating the missing dataset could be controlled and the regenerated dataset could be as close as possible to the missing dataset, the Indirect approach is better and gives higher accuracy, as can be seen from the 5-fold cross validation accuracies achieved from training the classifier on the complete dataset.
 
@@
 \begin{center}
-	\begin{tabular}{lll}
-		\multicolumn{1}{c}{\bf Fold}  &\multicolumn{1}{c}{\bf Accuracy of Direct Approach} &\multicolumn{1}{c}{\bf Accuracy of Indirect Approach} 
+	\begin{tabular}{llll}
+		\multicolumn{1}{c}{\bf Fold}  &\multicolumn{1}{c}{\bf Accuracy of Direct Approach} &\multicolumn{1}{c}{\bf Accuracy of Indirect Approach} &\multicolumn{1}{c}{\bf Best Case Accuracy}
 		\\ \hline \\
-		Fold 1   &0.5714 &0.5648 \\
-		Fold 2   &0.5914 &0.5714 \\
-		Fold 3   &0.61 &0.59 \\
-		Fold 4   &0.61   &0.61 \\
-		Fold 5   &0.5933   &0.5767 \\
-		Average Accuracy   &0.5952 &0.5826\\
+		Fold 1   &.5714 &0.5482 &0.598 \\
+		Fold 2   &0.5914 &0.588 &0.6512 \\
+		Fold 3   &0.61 &0.58 &0.6467 \\
+		Fold 4   &0.61   &0.6133 &0.6567 \\
+		Fold 5   &0.5933   &0.58 &0.6067 \\
+		Average Accuracy   &0.5952 &0.5819 &0.6318\\
 	\end{tabular}
@@
 
-FINAL RESULT
-
 \subsubsection*{References}
@@
 \small{
-[1] http://scikit-learn.org/stable/modules/preprocessing.html
+[1]Scikit-learn: Machine Learning in Python, Pedregosa et al., JMLR 12, pp. 2825-2830, 2011.
 
-[2] http://scikit-learn.org/stable/modules/generated/sklearn.decomposition.PCA.html
+[2] http://scikit-learn.org/stable/modules/preprocessing.html
 
-[3] http://scikit-learn.org/stable/modules/feature\_selection.html
+[3] http://scikit-learn.org/stable/modules/generated/sklearn.decomposition.PCA.html
 
-[4] http://scikit-learn.org/stable/modules/svm.html
+[4] http://scikit-learn.org/stable/modules/feature\_selection.html
 
-[5] http://scikit-learn.org/stable/modules/linear\_model.html
+[5] http://scikit-learn.org/stable/modules/svm.html
 
-[x]Scikit-learn: Machine Learning in Python, Pedregosa et al., JMLR 12, pp. 2825-2830, 2011.
+[6] http://scikit-learn.org/stable/modules/linear\_model.html
+
+[7] http://scikit-learn.org/stable/modules/generated/sklearn.linear\_model.MultiTaskLassoCV.html
 
 }
-
 \end{document}

### 2015-12-19 src/pc_multiclassLasso.py

@@ -70,24 +70,24 @@ X_train_reduced = combined_features.transform(X_train_scaled)
 X_test_reduced = combined_features.transform(X_test_scaled)
 
 ## Create K folds
-#k_fold = KFold(Y_train_raw.shape[0], n_folds=4)
-#for train, test in k_fold:
-#    X1 = X_train_reduced[train]
-#    Y1 = Y_train_raw[train]
-#    
-#    X2 = X_train_reduced[test]
-#    Y2 = Y_train_raw[test]    
-#
-#    ## Train Classifiers on fold
-#    mcl_clf = MultiTaskLasso(alpha=.6257)
-#    mcl_clf.fit(X1, Y1)
-#
-#
-#    ## Score Classifiers on fold
-#
-#    mcl_clf_score = mcl_clf.score(X2, Y2)
-#
-#    print "MultiTaskLasso:  ", mcl_clf_score
+k_fold = KFold(Y_train_raw.shape[0], n_folds=10)
+for train, test in k_fold:
+    X1 = X_train_reduced[train]
+    Y1 = Y_train_raw[train]
+    
+    X2 = X_train_reduced[test]
+    Y2 = Y_train_raw[test]    
+
+    ## Train Classifiers on fold
+    mcl_clf = MultiTaskLasso(alpha=.3)
+    mcl_clf.fit(X1, Y1)
+
+
+    ## Score Classifiers on fold
+
+    mcl_clf_score = mcl_clf.score(X2, Y2)
+
+    print "MultiTaskLasso:  ", mcl_clf_score
 
 
 
